Classless Java

### 2015-11-05 paper/sections/Introduction.tex
Notes for the introduction

>>>>

\bruno{Notes for the introduction.}

Default methods were introduced in Java; they allow a simple form 
of multiple-inheritance similar to traits. However, trying to 
use default methods to simulate multiple inheritance quickly becomes 
cumbersome

\item interfaces have no constructors; classes are still required to
create objects, leading to boilerplate code for initialization.

\item interfaces do not have instance fields; using setter and getter 
methods is a way out of this; but this requires tedious boilerplate 
classes that latter implement those methods.

\item Useful methods, general purpose methods, such as $clone$, or 
\emph{fluent} setters~\cite{} can only be defined 
with access to the internal state, which is not available in 
an interface. Moreover such methods require special care in the 
presence of subtypes.

This paper proposes \emph{concrete interfaces}: a simple extension 
to Java interfaces where all interface methods have an implementation. 
Concrete interfaces have a single constructor that is derived from the 
interface; they support various common utility methods (such as getters 
and setters, or clone methods) without boilerplate; and they automatically 
they with utility methods in the presence of subtyping.

To formalize concrete interfaces, we propose FeatherweightConcrete (FC): 
a FeatherweightJava-style calculus, which captures the essence 
of interfaces with default methods. The semantics of concrete interfaces 
is given as a type-directed translation from FC to FC itself. 
In the resulting FC code all concrete interfaces are translated into 
regular FC (and Java) interfaces with default methods. The translation 
is proved to be type-preserving, ensuring that the tranlation does 
not introduce new errors. One interesting aspect of the theorem is that 
if we ignore the concrete annotations, the program still type-checks 
under the regular typing rules of FC.

We implement concrete interfaces, purely using Java annotations. As such 
no new syntax is required, and existing Java tools (such as IDE's) work 
with our implementation.
